\section*{Список литературы}

\addcontentsline{toc}{chapter}{Список литературы}

$\quad$ Левин М.И., Левина Е.А. Моделирование лоббистской деятельности.
Экономика и Математические Методы, том 37, выпуск 3, стр. 76-96 (2001).

Полищук Л.И. Экономическая эффективность и присвоение ренты: 
анализ спонтанной приватизации. Экономика и Математические Методы, 
том 32, выпуск 2, стр. 5-24 (1996).

Полтерович В.М. Факторы коррупции. Экономика и Математические Методы,
том 34, выпуск 3, стр. 30-39 (1998).

Савватеев А.В. Роль экстерналий в формировании равновесного уровня коррупции 
в производстве. В серии \лк Научные доклады РПЭИ\пк, WP \# 2K/04 (2000).

Савватеев А.В. Оптимальные стратегии подавления коррупции. Экономика и 
Математические Методы, выпуск 39, стр. 62-75 (2003).

Сатаров Г.А., Левин М.И., Цирик М.Л. Россия и коррупция: кто кого? Доклад в 
Российской Газете за 19 февраля 1998 года (1998).

Acemoglu, D.  Reward Structure and the Allocation of Talent. European 
Economic Review, vol. 39, pp. 17-33 (1995).

Alchian, A. Rent. In: The New Palgrave. A Dictionary of Economics. 
Edited by John Eatwell at al, vol. 4, pp. 141-143. The Macmillan 
Press Ltd (1991).

Aslund, A. How Russia Became a Market Economy. Brookings Institution, 
Washington, D.C. (1995).

Aumann, R.J. Acceptable points in general cooperative $n$-person
games. Contributions to the theory of games, Volume 4. Princeton
University Press (1959).

Bardhan, P. Corruption And Development: A Review of Issues.
Journal of Economic Literature, Vol. 35, 1320-1346 (1997).

Basu, S. and Li D.D. Corruption in Transition. William Davidson Institute
Working Paper Series, WP \# 161 (1998). 

Bicchieri C,, and Rovelli C. Evolution and Revolution. Rationality
and Society, Vol. 7, 201-224 (1995).

Chander P., Wilde L. Corruption in Tax Administration. Journal of Public 
Economics, vol. 49, 333-349 (1992).

Ericson, R. On An Allocative Role of The Soviet Second Economy. In: P.
Desai (ed). Marxism, Central Planning, and The Soviet Economy.
Cambridge, M.A.: The MIT Press (1983).

Grossman, G.M., and Helpman, E. Protection for sale. The American Economic 
Review, vol. 84, No. 4, 833-850 (1994).

Guriev, S. A Theory of Informative Red Tape. New Economic School, 
mimeo, June (2000).

Hindriks J., Keen M., Muthoo A. Corruption, extortion and evasion.
Journal of Public Economics, vol. 74, 395-430 (1999).

Holmstrom, B. Moral Hazard in Teams. Bell Journal of Economics,
324-340 (1982).

Ichiishi, T. The cooperative nature of the firm. Cambridge University
Press (1993).

Krueger, A.O. The Political Economy of Rent-Seeking Society. The American
Economic Review, vol. 64, pp. 291-303 (1974).

Li, D.D. A theory of Ambiguous Property Rights in Transition Economies: 
The Case of the Chinese Non-State Sector. Journal of Comparative 
Economics, vol. 23, 1--19 (1996).

Lu, D. The Enterpreneurs Who Do Both: Production and Rent-seeking. Juornal of
Economic Behavior and Organization, vol. 23, pp. 93-98 (1994).

Lui, F.T. A Dynamic Model of Corruption Deterrence. Journal of Political
Economy, vol. 31, 215-236 (1986).

Magnus, J.R., Polterovich, V.M., Danilov, D.L., and Savvateev, A.V. Tolerance
of Cheating: An Analysis Across Countries. Journal of Economic Education,
vol. 33, no. 2, pp. 125-135 (2002).

Malcomson, J-M. Rank-Order Contracts for the Principal with Many
Agents. The Review of Economic Studies, Volume 53, pp. 807-817 (1986).

Marshall, A.W. and I. Olkin. Inequalities: Theory of Majorization and Its 
Applications. Academic Press (1979).

Mas-Colell, A, Whinston, M.D., and Green, J. Microeconomic Theory.
Oxford University Press (1995).

Mitra, D. Endogenous Lobby Formation and Endogenous Protection: A Long-Run
Model of Trade Policy Determination. The American Economic Review,
vol. 89, No. 5, 1116-1134 (1999).

Mohtadi H., Roe T. Growth, Lobbying and Public Goods. European Journal of 
Political Economy, Vol. 14, 453-473 (1998).

Mookherjee D., Png I. Optimal Auditing, Insurance, and Redistribution.
Quarterly Journal of Economics, vol. 104, 399-415 (1989).

Murphy, K.M., Shleifer A., and Vishny, R.W. The Allocation of Talent: 
Implication for Growth. Quarterly Journal of Economics, vol. 106, 
503-31 (1991).

Murphy, K.M., Shleifer A., and Vishny, R.W. Why Is Rent-Seeking So Costly 
to Growth? American Economic Review, vol. 83, No. 2, 409--414 (1993).

Myerson, R.B., Warneryd K. Contests with Population Uncertainty. 
Stockholm Institute for Transition Economy, mimeo (1996).

Pecorino, P. Is There a Free-Rider Problem in Lobbying? Endogenous Tariffs,
Trigger Strategies, and the Number of Firms. The American Economic Review,
vol. 88, No. 3, 652-660 (1998).

Polishchuk L., Savvateev A. Spontaneous (Non)Emergence of Property Rights.
New Economic School, mimeo (1997).

Polterovich, V. Rent-Seeking, Tax Policy, and Economic Growth. Working paper
WP \# 2001/027, New Economic School, Moscow (2001).

Rose-Ackerman, S. "The Economics of Corruption". Journal of Public
Economics, vol. 4, 187-203 (1975).

Rose-Ackerman, S. Corruption: A Study in Political Economy. New York, 
Academic Press, Inc. (1978).

Savvateev, A. Production And Rent-seeking Behavior. Working Paper BSP/98/001, 
New Economic School, CEMI (1998).

Shleifer, A., and Treisman, D. Without a map: Political tactics and 
Economic Reform in Russia. MIT Press (2000).

Shleifer A., and Vishny R.W. Corruption. Quarterly Journal of Economics, 
CVIII, pp. 599-617 (1993).

Skaperdas, S. Contest Success Functions. Economic Theory, vol. 7, 
pp. 283-90 (1996).

Sonin, K. Why the Rich May Favor Poor Protection of Property Rights. 
Journal of Comparative Economics, forthcoming (2002).

Sun G-Z., and Ng Y-K. The effect of number and size of interest groups on 
social rent dissipation. Public Choice, Vol. 101, 251-265 (1999).

Tarski, A. A Lattice-Theoretical Fixpoint Theorem and Its
Applications. Pacific Journal of Mathematics, 5, 285-309 (1955).

Tirole J. A Theory of Collective Reputations With Applications to The
Persistence of Corruption And to Firm Quality. Institut d'Economie
Industrielle, Toulouse, MIT and Ceras, Paris (1996).

Topkis, Donald M. Minimizing a Submodular Function on a Lattice.
Operations Research, 26, 305-321 (1978).

Topkis, Donald M. Supermodularity and Complementarity. Princeton University
Press, Princeton (1998).

Transparency International. Corruption Perception Index~--- 2001. Журнал
\лк Чистые Руки\пк, 84-86, выпуск 5 (2002).

Tullock, G. Efficient Rent Seeking. In J.M. Buchanan, P.D. Tollison, and G. 
Tullock (eds.), Towards a Theory for Rent-Seeking Society,  pp. 97-112. 
Texas A\&M University Press (1980).

Tullock, G. Rent-seeking. In: The New Palgrave. A Dictionary of
Economics. Edited by John Eatwell at al, vol. 4, pp. 147-149.
The Macmillan Press Ltd (1991).

Vasin A., Panova E. Tax Collection and Corruption in Fiscal Bodies.
EERC WP Series, WP \# 99/10 (2000).

Warneryd, K. Rent, Risk, and Replication Political Contests
and Preference Adaption. WP 377, Working Paper Series in
Economics and Finance. October (1995).

Wei, S-J. Why Is Corruption So Much More Taxing Than Tax? Arbitrariness 
Kills. NBER Working Paper Series, WP \# 6255 (1997).                                         
                                        
Zhuravskaya E, Ponomareva, M. Federal Tax Arrears: Liquidity Problems,
Federal Subsidies, or Regional Protection? Mimeo, CEFIR and CEPR (2000).

Zhuravskaya E, Orlov E, Paltseva E. Determinants of government subsidies 
to industrial firms in Russia: firm-level evidence. CEFIR Working
Paper (2001).